% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Rui Li}

\basicInfo{
  \email{leereborn92929@gmail.com} \textperiodcentered\ 
  \phone{613-277-1820} \textperiodcentered\ 
  \linkedin[ruili]{https://www.linkedin.com/in/rui-li-a193a799/}\textperiodcentered\
  \github[leereborn]{https://github.com/leereborn}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Master of Computer Science Specializing in Data Science}}{Sept. 2018 -- Aug. 2020}
\datedsubsection{Carleton University}{Ottawa, ON, Canada}
\begin{itemize}
	\item Graduated with GPA of 11.4/12.
	\item Master's Thesis: An Investigation of Attention Mechanisms in Graph Convolutional Networks applied to Link Prediction Problems
	%\item Relevant courses: Machine Learning, Deep Learning and Reinforcement Learning, Natural Language Processing.
\end{itemize}
 

\datedsubsection{\textbf{Bachelor of Computer Science Honours with Distinction}}{Sept. 2014 -- Apr. 2018}
\datedsubsection{Carleton University}{Ottawa, ON, Canada}

\section{\faCogs\ Technical Skills}
\begin{itemize}
	\item Programming Language: Python, Java, Javascript
	\item Library: Tensorflow, NodeJS, ReactJS
	\item Database: SQL, MongoDB
	\item Software: Git, Linux, \LaTeX, Jenkins
	\item Cloud Technology: AWS EC2, AWS Lambda
\end{itemize}

\section{\faCogs\ Experience}
\datedsubsection{\textbf{Carleton University}}{Ottawa, ON, Canada}
\role{Research and Teaching Assistant}{Sept. 2018 -- Aug. 2020}
\begin{itemize}
	\item Conducted research on Graph Convolutional Networks in Prof. Tony White's Complex Adaptive System lab.
	\item Courses that I have been a Teaching Assistant for include: Abstract Data Types and Algorithms, Neural Networks, and Information Retrieval and Recommender Systems.
\end{itemize}

\datedsubsection{\textbf{Espial Group}}{Ottawa, ON, Canada}
\role{Co-op Software Developer}{Jan. 2017 -- Aug. 2017}
\begin{itemize}
	\item Worked in an agile team to develop the test automation infrastructure.
	\item Developed various Javascript unit test scripts for testing set-top box UI level APIs.
	\item Automated the nightly build test process so that unit tests are executed and results are published on the Confluence wiki automatically each night.
	%\item The test automation infrastructure saved the QA team manual testing and reporting effort.
\end{itemize}

\datedsubsection{\textbf{Corsa Technology}}{Ottawa, ON, Canada}
\role{Co-op Software Developer}{Sept. 2016 -- Dec. 2016}
\begin{itemize}
	\item Developed Python scripts to automate sanity tests for SDN switch products.
	\item Implemented the web server and the front-end UI for executing the test scripts. 
	\item Reduced the possibility that defective products were shipped to customers by 30\%.
\end{itemize}

\section{\faUsers\ Projects}
\datedsubsection{Online Python Playground}{Dec. 2020}
\begin{itemize}
	\item Allows users to run Python script conveniently from browser. 
	\item The front-end UI is implemented in HTML, CSS, and JQuery.
	\item The server consists of two microservices, one for executing python and the other for routing incoming requests. The two microservices are deployed in two different AWS Lambda functions.
	\item Check out the demo at: \url{https://s5t7bw78d5.execute-api.us-east-2.amazonaws.com/dev/demo/python-playground}  
\end{itemize}

\datedsubsection{Unix Log Analyzer Web App}{Mar. 2018}
\begin{itemize}
	\item Implemented the RESTful server using Node and MongoDB which allows users to upload and store Unix-like OS logs.
	\item Designed and implemented interactive React UI components for users to query and visualize logs. 
\end{itemize}

\section{\faInfo\ Extra-curricular}
\datedline{CSearch Conference}{Oct. 2020}
\begin{itemize}
	\item Invited to attended Computing Student Research Conference (CSearch) 2020.
	\item Delivered Poster presentation on application of graph attention networks to link prediction problems.
\end{itemize}
%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
