% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Rui Li}

\basicInfo{
  \email{leereborn92929@gmail.com} \textperiodcentered\ 
  \phone{613-277-1820} \textperiodcentered\ 
  \linkedin[ruili]{https://www.linkedin.com/in/rui-li-a193a799/}\textperiodcentered\
  \github[leereborn]{https://github.com/leereborn}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Master of Computer Science Specializing in Data Science}}{Sept. 2018 -- Oct. 2020}
\datedsubsection{Carleton University}{Ottawa, ON, Canada}
\begin{itemize}
	\item Graduated with GPA of 11.4/12.
	\item Master's Thesis: An Investigation of Attention Mechanisms in Graph Convolutional Networks applied to Link Prediction Problems
	%\item Relevant courses: Machine Learning, Deep Learning and Reinforcement Learning, Natural Language Processing.
\end{itemize}
 

\datedsubsection{\textbf{Bachelor of Computer Science Honours with Distinction}}{Sept. 2014 -- Apr. 2018}
\datedsubsection{Carleton University}{Ottawa, ON, Canada}

\section{\faCogs\ Technical Skills}
\begin{itemize}
	\item Programming Language: Python, Java, Javascript
	%\item Web: HTML, CSS, JQuery, Node.js, Express.js, React.js
	\item Web: HTML, CSS, Node.js, Express.js, React.js
	%\item Database: SQL, MongoDB
	\item Software development: Git, Linux, SSH, Jenkins, Agile, JIRA, VSCode
	\item Cloud Technology: AWS EC2, AWS Lambda
\end{itemize}

\section{\faCogs\ Experience}
\iffalse
\datedsubsection{\textbf{Carleton University}}{Ottawa, ON, Canada}
\role{Research and Teaching Assistant}{Sept. 2018 -- Aug. 2020}
\begin{itemize}
	\item Conducted research on Graph Convolutional Networks in Prof. Tony White's Complex Adaptive System lab.
	\item Led tutorials and laboratory sections. 
	\item Explained computer science concepts to students using examples and analogies. 
	\item Students who often attended my office hour improved their score by 10\% on average.  
	%\item Courses that I have been a Teaching Assistant for include: Abstract Data Types and Algorithms, Neural Networks, and Information Retrieval and Recommender Systems.
\end{itemize}
\fi

\datedsubsection{\textbf{Espial Group}}{Ottawa, ON, Canada}
\role{Co-op Software Developer}{Jan. 2017 -- Aug. 2017}
\begin{itemize}
	\item Worked in an \textbf{agile} team to develop the test automation infrastructure.
	\item Developed various \textbf{Javascript} unit test scripts for testing set-top box APIs.
	\item Automated the nightly build test process on \textbf{Jenkins} so that unit tests are executed and results are published on the Confluence wiki automatically each night.
	%\item The test automation infrastructure saved the QA team manual testing and reporting effort.
\end{itemize}

\datedsubsection{\textbf{Corsa Technology}}{Ottawa, ON, Canada}
\role{Co-op Software Developer}{Sept. 2016 -- Dec. 2016}
\begin{itemize}
	\item Developed \textbf{Python} scripts to automate sanity tests for SDN switch products.
	%\item Implemented the web server and the front-end UI for executing the test scripts.
	\item Used Iperf3 to generate network traffic for port path tests.
	\item Used Paramiko to ssh to switches for configurations
	\item Implemented Network Address Translation (NAT) in order to send the traffic through.  
	\item Reduced the possibility that defective products were shipped to customers by 30\%.
\end{itemize}

\section{\faUsers\ Self-driven Projects}
\datedsubsection{React TODO List App}{Apr. 2021}
\begin{itemize}
	\item Users can add, delete, and view the detail of each task
	\item Broke the UI into \textbf{functional components} of form, table, navbar, and detail page 
	\item Used \textbf{React-Router} to turn the app into single page application
	\item Lifted the content state up so that the content can be share top-down through components.
	\item \textbf{Check out the demo} at: \url{https://leereborn.github.io/react-TODO-list/}
\end{itemize}

\datedsubsection{Stock Trading Simulation}{Mar. 2021}
\begin{itemize}
	\item Implemented RESTful APIs for authentication, portfolio management, and stock trading using \textbf{ExpressJS}.
	\item Designed user and stock \textbf{MongoDB} schema and implemented CRUD using Mongoose.
	\item Developed user authentication functionalities using Passport.
	\item \textbf{Check out the project} at: \url{https://github.com/leereborn/stock-tracking}
\end{itemize}

\datedsubsection{Online Python Playground}{Dec. 2020}
\begin{itemize}
	\item Allows users to run Python script conveniently from the browser. 
	\item The front-end UI is implemented in HTML, CSS, and JQuery.
	\item The server consists of two \textbf{microservices}, one for executing python and the other for routing incoming requests. The two microservices are deployed in two different \textbf{AWS Lambda} functions.
	\item The two backend microservices are implemented in \textbf{Node} and \textbf{Python}.
	\item \textbf{Check out the demo} at: \url{https://s5t7bw78d5.execute-api.us-east-2.amazonaws.com/dev/demo/python-playground}  
\end{itemize}

\iffalse
\datedsubsection{Document File Search Engine}{Mar. 2018}
\begin{itemize}
	\item Implemented document parser using Tika to parse documents in given directories and stored contents and metadata into Mongodb.
	\item Developed document analyzer in \textbf{Java} using Lucene to index and score the stored documents given a query string.
	\item Implemented RESTful APIs using \textbf{Spring Boot} to provide search results.
\end{itemize}
\fi

\iffalse
\datedsubsection{Unix Log Analyzer Web App}{Mar. 2018}
\begin{itemize}
	\item Implemented the RESTful server using Node and MongoDB which allows users to upload and store Unix-like OS logs.
	\item Designed and implemented interactive React UI components for users to query and visualize logs. 
\end{itemize}
\fi

\iffalse
\section{\faInfo\ Extra-curricular}
\datedline{CSearch Conference}{Oct. 2020}
\begin{itemize}
	\item Invited to attended Computing Student Research Conference (CSearch) 2020.
	\item Delivered Poster presentation on application of graph attention networks to link prediction problems.
\end{itemize}
\fi
%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
